Combining living and fossil taxa into phylogenies: the missing data issue

### 2015-07-27 Manuscript/MPESubmission/Revision/TEM_revised_manuscript.tex
Standardised Bhattacharyya coefficient across whole work

We measured similarities among the distributions of the different metrics scores (Normalised Robinson-Foulds and Normalised Triplets metric) using the Bhattacharyya Coefficient \citep{Bhattacharyya}.
The Bhattacharyya Coefficient is the probability of overlap between two distributions \citep{Bhattacharyya} (see Appendix B for calculation details).
Note that this is comparable to performing a two-sided t-test, but we use the Bhattacharyya Coefficient here because we are comparing whole distributions not just their means.
To assess the effect of our missing data parameters, we calculated the Bhattacharyya Coefficient between the distributions of the different metrics scores (Normalised Robinson-Foulds and Normalised Triplets metric) for each pairwise combination of missing data parameters ($M_{L}$, $M_{F}$, $N_{C}$) and parameter states (0\%, 10\%, 25\%, 50\%, 75\% and 100, 90, 75, 50, 25 characters), i.e. $M_{L}$ = 0\%, $M_{F}$ = 0\%, $N_{C}$ = 100; $M_{L}$ = 10\%, $M_{F}$ = 0\%, $N_{C}$ = 100 etc. (see Figure 2 for more details).
This resulted in 7875 pairwise comparisons (a triangular matrix with $3^5$$\times$$3^5$ cells).
We performed this procedure separately for each tree inference and uncertainty method.
When two combinations of missing data parameters have a similar ability to recover the ``best'' tree topology the Bhattacharyya Coefficient will be close to one.
Conversely, if the two combinations of missing data parameters differ, the Bhattacharyya Coefficient will be close to zero.
Because of the difficulties to represent so many pairwise comparisons in a meaningful way, we summarized as a heat map of Bhattacharyya Coefficients (see Figure 6).
In this type of figures, parameters that have similar or different effects on recovering the ``best'' topology (rather good or bad effects) will be denoted by similar colour patches in the heat map representation of these comparisons (see Figure 6).

>>>>

We measured similarities among the distributions of the different metrics scores (Normalised Robinson-Foulds and Normalised Triplets metric) using the Bhattacharyya Coefficient \citep{Bhattacharyya}.
The Bhattacharyya Coefficient is the probability of overlap between two distributions \citep{Bhattacharyya} (see Appendix B for calculation details).
Note that this is comparable to performing a two-sided t-test, but we use the Bhattacharyya Coefficient here because we are comparing whole distributions not just their means.
When the Bhattacharyya Coefficient between two distributions is $<$0.05, the distributions are significantly different.
When this coefficient is $>$0.95 both distributions are significantly similar.
Values in between these two threshold just show the probability of overlap between the distributions but are not conclusive to assess the similarity or differences between the distributions.
To assess the effect of our missing data parameters, we calculated the Bhattacharyya Coefficient between the distributions of the different metrics scores (Normalised Robinson-Foulds and Normalised Triplets metric) for each pairwise combination of missing data parameters ($M_{L}$, $M_{F}$, $N_{C}$) and parameter states (0\%, 10\%, 25\%, 50\%, 75\% and 100, 90, 75, 50, 25 characters), i.e. $M_{L}$ = 0\%, $M_{F}$ = 0\%, $N_{C}$ = 100; $M_{L}$ = 10\%, $M_{F}$ = 0\%, $N_{C}$ = 100 etc. (see Figure 2 for more details).
This resulted in 7875 pairwise comparisons (a triangular matrix with $3^5$$\times$$3^5$ cells).
We performed this procedure separately for each tree inference and uncertainty method.
When two combinations of missing data parameters have a similar ability to recover the ``best'' tree topology the Bhattacharyya Coefficient will be close to one.
Conversely, if the two combinations of missing data parameters differ, the Bhattacharyya Coefficient will be close to zero.
Because of the difficulties to represent so many pairwise comparisons in a meaningful way, we summarized as a heat map of Bhattacharyya Coefficients (see Figure 6).
In this type of figures, parameters that have similar or different effects on recovering the ``best'' topology (rather good or bad effects) will be denoted by similar colour patches in the heat map representation of these comparisons (see Figure 6).
